%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template for CV/Resume
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Author:
% Claud D. Park <posquit0.bj@gmail.com>
% http://www.posquit0.com
%
%
% Adapted to be an Rmarkdown template by Mitchell O'Hara-Wild
% 23 November 2018
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%
%-------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
% A4 paper size by default, use 'letterpaper' for US letter
\documentclass[11pt,a4paper,]{awesome-cv}

% Configure page margins with geometry
\usepackage{geometry}
\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}


% Specify the location of the included fonts
\fontdir[fonts/]

% Color for highlights
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight

\definecolor{awesome}{HTML}{075aa3}

% Colors for text
% Uncomment if you would like to specify your own color
% \definecolor{darktext}{HTML}{414141}
% \definecolor{text}{HTML}{333333}
% \definecolor{graytext}{HTML}{5D5D5D}
% \definecolor{lighttext}{HTML}{999999}

% Set false if you don't want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{true}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}

\def\endfirstpage{\newpage}

%-------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%-------------------------------------------------------------------------------
% Available options: circle|rectangle,edge/noedge,left/right

\name{}{Allison R Mason, PhD}

\position{Microbiologist}

\pronouns{she/her}
\email{\href{mailto:masona13@outlook.com}{\nolinkurl{masona13@outlook.com}}}
\homepage{amason30.github.io}
\orcid{0000-0003-1339-1592}
\github{amason30}
\linkedin{allisonmason}

% \gitlab{gitlab-id}
% \stackoverflow{SO-id}{SO-name}
% \skype{skype-id}
% \reddit{reddit-id}


\usepackage{booktabs}

\providecommand{\tightlist}{%
	\setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

%------------------------------------------------------------------------------



% Pandoc CSL macros

\begin{document}

% Print the header with above personal informations
% Give optional argument to change alignment(C: center, L: left, R: right)
\makecvheader

% Print the footer with 3 arguments(<left>, <center>, <right>)
% Leave any of these blank if they are not needed
% 2019-02-14 Chris Umphlett - add flexibility to the document name in footer, rather than have it be static Curriculum Vitae
\makecvfooter
  {March 2024}
    { Allison R Mason, PhD~~~·~~~Curriculum Vitae}
  {\thepage~ of \pageref{LastPage}~}


%-------------------------------------------------------------------------------
%	CV/RESUME CONTENT
%	Each section is imported separately, open each file in turn to modify content
%------------------------------------------------------------------------------



\makeatletter
\def\@sectioncolor{\color{awesome}}
\makeatother

\definecolor{specialblue}{RGB}{7, 90, 163}

\hypertarget{summary}{%
\section{Summary}\label{summary}}

I'm a microbial ecologist with experience in computational biology and
management of multivariate projects. My research encompasses soil
microbial ecology and terrestrial vertebrate decomposition. I have
experience with multiple programming languages, with an expertise in R
and execution of microbiome data analysis. I'm passionate about open
source science, reproducible research, and teaching computational skill
to individuals of all levels.

\hypertarget{skills-and-expertise}{%
\section{\texorpdfstring{\faCogs Skills and
Expertise}{Skills and Expertise}}\label{skills-and-expertise}}

\begin{table}[!h]
\centering\begingroup\fontsize{9}{11}\selectfont

\begin{tabular}{>{\centering\arraybackslash}m{4.85cm}>{\centering\arraybackslash}m{4.85cm}>{\centering\arraybackslash}m{4.85cm}}
\toprule
\textcolor[HTML]{075aa3}{\textbf{Computational}} & \textcolor[HTML]{075aa3}{\textbf{Research}} & \textcolor[HTML]{075aa3}{\textbf{Laboratory}}\\
\midrule
\textcolor[HTML]{7f7f7f}{R -- R Markdown -- R Package Development -- Quarto --Git/Github -- Conda -- Unix/zsh} & \textcolor[HTML]{7f7f7f}{Soil sampling/Field research -- Amplicon Sequencing -- Data Analysis/Visualization Soil microbiome/necrobiome -- Metatranscriptomics -- Biostatistics -- Reproducible Research -- Machine learning} & \textcolor[HTML]{7f7f7f}{DNA/RNA extraction -- PCR/qPCR/RT-qPCR -- Cell culture -- Fluorometric assays -- Cell enumeriation -- media/solution preparation -- Cloning -- Gel electrophoresis -- Western blot}\\
\bottomrule
\end{tabular}
\endgroup{}
\end{table}

\hypertarget{experience}{%
\section{\texorpdfstring{\faBarChart Experience}{Experience}}\label{experience}}

\begin{cventries}
    \cventry{Schloss Lab}{Postdoctoral Research Fellow (remote)}{Univeristy of Michigan}{Sep 2022 - present}{\begin{cvitems}
\item Development of an R package for microbiome and multi-omics research/data analytics.
\item Project Team Lead, including oversight and management of progress for masters-level bioinformaticians.
\item Expanding foundational knowledge of metabolomics.
\item Cultivating skills in reproducible research, markdown, git/github, quarto, data analysis. 
\item Teaching computational skills to coding beginners at institutional workshops.
\end{cvitems}}
    \cventry{DeBruyn Lab}{Graduate Research Assistant}{University of Tennessee-Knoxville}{Aug 2017 - Aug 2022}{\begin{cvitems}
\item Conducted DNA extractions and 16S/ITS amplicon sequencing to characterize soil microbial succession during terrestrial vertebrate decomposition.
\item Led a project characterizing soil microbial gene expression via metatranscriptomics. 
\item Managed multivariate datasets while gaining computational skills including Mothur, R, unix, conda, etc.
\item Developed and executed methods for soil and fluid samples collection.
\item Measured soil physical and chemical parameters via soil extractions and fluorometric assays.
\item Managed and collaborated on multiple field experiments: responsible for preparing and executing field sampling.
\item Navigated, communicated, and collaborated with interdisciplinary research groups to accomplish grant aims and publication. 
\end{cvitems}}
    \cventry{Ohio Water Microbiology Laboratory}{Intern (biology)}{United States Geological Survey}{Jul 2015 - Jul 2017}{\begin{cvitems}
\item Handled and prepared water and environmental samples from across the country for various tests such as: enumeration of enterococci, aerobic endospores, and virus plaques (1601 and 1602) and multiple source tracking.
\item Analyzed and reported test results.
\item Prepared solutions and media and maintained the lab.
\end{cvitems}}
    \cventry{Boris-Lawrie Lab}{Undergraduate Researcher}{The Ohio State University}{Jan 2014 - May 2015}{\begin{cvitems}
\item Learned about protein-protein interactions to understand a suspected gene splicing product.
\item Applied techniques such as cell culture and gene cloning (plasmid and site directed mutagenesis). 
\item Acquired skills in RT-PCR, western blotting, gel electrophoresis, and maintaining cell lines.
\end{cvitems}}
\end{cventries}

\hypertarget{education}{%
\section{\texorpdfstring{\faUniversity Education}{Education}}\label{education}}

\begin{cventries}
    \cventry{Department of Microbiology}{PhD Microbiology}{University of Tennessee-Knoxville}{Aug 2017 - Aug 2022}{\begin{cvitems}
\item Advisor: Jennifer DeBruyn
\end{cvitems}}
    \cventry{College of Arts and Sciences}{BS Microbiology}{The Ohio State University}{Aug 2013 - May 2017}{\begin{cvitems}
\item Minor: Forensic Science
\end{cvitems}}
\end{cventries}

\hypertarget{teaching-and-mentorship}{%
\section{\texorpdfstring{\faBook Teaching and
Mentorship}{Teaching and Mentorship}}\label{teaching-and-mentorship}}

\large \textbf{\textcolor{specialblue}{Teaching}}

\begin{cventries}
    \cventry{U-M Carpentries}{Workshop on R, the Unix Shell, \& Git/GitHub}{}{Dec 2023}{}\vspace{-4.0mm}
    \cventry{U-M Carpentries}{Workshop on R, the Unix Shell, \& Git/GitHub}{}{Mar 2023}{}\vspace{-4.0mm}
    \cventry{University of Tennessee-Knoxville}{BIOL160 \textit{Cellular and Molecular Biology}}{Department of Biochemistry \& Cellullar \& Molecular Biology}{Aug 2022 - Jan 2023}{}\vspace{-4.0mm}
    \cventry{University of Tennessee-Knoxville}{MICR229 \textit{General Microbiology Laboratory}}{Department of Biological Sciences}{Aug 2022 - Jan 2023}{}\vspace{-4.0mm}
    \cventry{University of Tennessee-Knoxville}{BIOL229 \textit{General Microbiology Laboratory}}{Department of Biological Sciences}{Aug 2021 - May 2022}{}\vspace{-4.0mm}
    \cventry{University of Tennessee-Knoxville}{BIOL229 \textit{General Microbiology Laboratory}}{Department of Biological Sciences}{Aug 2018 - Jan 2019}{}\vspace{-4.0mm}
    \cventry{University of Tennessee-Knoxville}{MICR210 \textit{Allied Health Microbiology}}{Department of Microbiology}{Aug 2017 - May 2018}{}\vspace{-4.0mm}
\end{cventries}

\large \textbf{\textcolor{specialblue}{Mentorship}}

\begin{cventries}
    \cventry{Department of Microbiology}{Brooke Tally (\textit{Honors Undergraduate Student})}{University of Tennessee-Knoxville}{2021 - 2022}{}\vspace{-4.0mm}
    \cventry{Department of Microbiology}{Victoria Beard (\textit{Honors Undergraduate Student})}{University of Tennessee-Knoxville}{2019 - 2020}{}\vspace{-4.0mm}
\end{cventries}

\hypertarget{publications}{%
\section{\texorpdfstring{\faFileText Publications}{Publications}}\label{publications}}

\small
\begin{enumerate}
\item \textbf{Allison R. Mason}, Lois S. Taylor, Naomi Gilbert, Steven S. Wilhelm, Jennifer M. DeBruyn. (2024). Soil microbial functional succession over one year of human decomposition. (\textit{in prep}). doi: \href{https://doi.org/}{}
\item \textbf{Allison R. Mason}, Hayden S. McKee-Zech, Dawnie W. Steadman, Jennifer M. DeBruyn. (2024). Environmental predictors impact microbial-based postmortem interval (PMI) estimation models within human decomposition soils. \textit{PLoS ONE (submitted)}. doi: \href{https://doi.org/}{}
\item Lois S. Taylor, \textbf{Allison R. Mason}, Hannah Noel, Michael Essington, Mary Davis, Veronica Brown, Dawnie W. Steadman, Jennifer M. DeBruyn. (2024). Transient hypoxia drives soil microbial community dynamics and biogeochemistry during human decomposition. \textit{FEMS Microbiology Ecology (in review)}. doi: \href{https://doi.org/}{}
\item \textbf{Allison R. Mason}, Lois S. Taylor, Jennifer M. DeBruyn. (2023). Microbial ecology of vertebrate decomposition in terrestrial ecosystems. \textit{FEMS Microbiology Ecology}. doi: \href{https://doi.org/https://doi.org/10.1093/femsec/fiad006}{https://doi.org/10.1093/femsec/fiad006}
\item \textbf{Allison R. Mason}, Hayden S. McKee-Zech, Katharina M. Hoeland, Mary C. Davis, Shawn R. Campagna, Dawnie W. Steadman, Jennifer M. DeBruyn. (2022). Body mass index (BMI) impacts soil chemical and microbial response to human decomposition. \textit{mSphere}. doi: \href{https://doi.org/https://doi.org/10.1128/msphere.00325-22}{https://doi.org/10.1128/msphere.00325-22}
\item Sarah W. Keenan, Alexandra L. Emmons, Lois S. Taylor, Gary Phillips, \textbf{Allison R. Mason}, Amy Z. Mundorff, Ernest C. Bernard, Jennifer M. DeBruyn. (2018). Spatial impacts of a multi-individual grave on microbial and microfaunal communities and soil biogeochemistry. \textit{PLoS ONE}. doi: \href{https://doi.org/https://doi.org/10.1371/journal.pone.0208845}{https://doi.org/10.1371/journal.pone.0208845}
\end{enumerate}

\hypertarget{presentations}{%
\section{\texorpdfstring{\faComments Presentations}{Presentations}}\label{presentations}}

\large \textbf{\textcolor{specialblue}{Talks}}

\begin{cventries}
    \cventry{Dissertation Defense}{An investigation of intrinsic and extrinsic factors that influence soil microbial succession during human decomposition.}{The University of Tennessee-Knoxville}{JUN 2022}{}\vspace{-4.0mm}
    \cventry{American Academy of Forensic Sciences (AAFS)}{Body mass index (BMI) impacts on soil chemical and microbial responses during human decomposition.}{Seattle, WA}{FEB 2022}{}\vspace{-4.0mm}
    \cventry{Women in STEM Symposium}{Human-associated Microbes in a Subsurface Human Decomposition System.}{University of Tennesse-Knoxville}{NOV 2018}{}\vspace{-4.0mm}
\end{cventries}

\large \textbf{\textcolor{specialblue}{Posters}}

\begin{cventries}
    \cventry{American Academy of Forensic Sciences (AAFS)}{Tuning microbial succession-based post-mortem interval  estimation models: effect of environmental parameters on model prediction.}{Seattle, WA}{FEB 2022}{}\vspace{-4.0mm}
    \cventry{American Academy of Forensic Sciences (AAFS)}{Inter-Individual Variation in Soil Chemistry and Microbial Ecology During Human Decomposition.}{Virtual}{FEB 2021}{}\vspace{-4.0mm}
    \cventry{Soil Science Society of America (SSSA)}{Variability in Soil Chemistry and Microbial Ecology During Early Stages of Human Decomposition.}{Virtual}{NOV 2020}{}\vspace{-4.0mm}
    \cventry{American Society of Microbiology (ASM)}{Assessment of Variability in Soil Chemistry and Microbial Ecology During Early Stages of Human Decomposition.}{Virtual}{JUN 2020}{}\vspace{-4.0mm}
    \cventry{Soil Science Society of America (SSSA)}{Spatial Impact of a Multi-individual Grave on Soil Biochemistry and Microbial Ecology.}{San Diego, CA}{JAN 2019}{}\vspace{-4.0mm}
    \cventry{American Society of Microbiology (ASM)}{Spatial Impact of a Multi-individual Grave on Soil Biochemistry and Microbial Ecology.}{Atlanta, GA}{JUN 2018}{}\vspace{-4.0mm}
\end{cventries}

\hypertarget{collaborator-products}{%
\section{\texorpdfstring{\faGroup Collaborator
Products}{Collaborator Products}}\label{collaborator-products}}

\small
\begin{enumerate}
\item \textbf{Allison R. Mason}, Lois S. Taylor, Jennifer M. DeBruyn (NOV 2022). [Metatranscriptomics Reveals Soil Microbial Functional Succession over One Year of Human Decomposition.](https://scisoc.confex.com/scisoc/2022am/meetingapp.cgi/Paper/142621) ASA, CSSA, SSSA International Annual Meeting NA
\item Lois S. Taylor, \textbf{Allison R. Mason}, Jennifer M. DeBruyn (FEB 2022). Seasonal comparisons between soil fungal and bacterial communities impacted by human decomposition. American Academy of Forensic Sciences (AAFS) NA
\item Dawnie W. Steadman, Jennifer M. DeBruyn, Shawn R. Campagna, \textbf{Allison R. Mason}, Hayden S. McKee, Katharina M. Hoeland, Sarah T. Schwing, Erin A. Patrick, Mary C. Davis, Amanda L. May, Thomas A. Delgado (FEB 2021). The Impact of Drugs on Human Decomposition and the Postmortem Interval: Insect, Scavenger and Microbial Evidence. National Institute of Justice (NIJ) Forensic Science Research and Development Symposium Virtual
\item Lois S. Taylor, \textbf{Allison R. Mason}, Jennifer M. DeBruyn (FEB 2021). Seasonal Differences in Soil Fungal Community Successional Patterns Impacted by Long-term Human Decomposition. American Academy of Forensic Sciences (AAFS) Virtual
\item Katharina M. Hoeland, Amanda L. May, Hayden S. McKee, Mary C. Davis, Sarah T Schwing, Thomas A. Delgado, Charity G. Owings, \textbf{Allison R. Mason}, Shawn R. Campagna, Jennifer M. DeBruyn, Dawnie W. Steadman, Russel L. Zaretzki (FEB 2021). Expanding Frontiers in Postmortem Toxicology: Drug Tracing in Different Postmortem Matrices during Human Decomposition using Ultra-High-Performance Liquid Chromatography-High Resolution Mass Spectrometry (UHPLC-HRMS). American Academy of Forensic Sciences (AAFS) Virtual
\item Amanda L. May, Katharina M. Hoeland, Hayden S. McKee, \textbf{Allison R. Mason}, Sarah T. Schwing, Charity G. Owings, Thomas A. Delgado, Mary C. Davis, Russel L. Zaretki, Jennifer M. DeBruyn, Dawnie W. Steadman, Shawn R. Campagna (FEB 2021). Using Metabolomics to Gain a Deeper Understanding of Human Decomposition. American Academy of Forensic Sciences (AAFS) Virtual
\item Hayden S. McKee, Charity G. Owings, Katharina M. Hoeland, Liesel Schneider, \textbf{Allison R. Mason}, Kristi Bugajski, Shawn R. Campagna, Jennifer M. DeBruyn, Dawnie W. Steadman (NOV 2020). Prescription Drugs detected in humans postmortem impact Phormia regina Meigen (Diptera: Calliphoridae) larval length. Entomological Society of America (ESA) 2020 Virtual
\item Victoria V. Beard, \textbf{Allison R. Mason}, Jennifer M. DeBruyn (APR 2020). Changes in Antibiotic Resistance of Soil Microbes During Human Decomposition. The Exhibition of Undergraduate Research and Creative Achievement (EUReCA) University of Tennesse-Knoxville
\item Katharina M. Hoeland, Amanda L. May, Hayden S. McKee, Thomas A. Delgado, Sarah T. Schwing, \textbf{Allison R. Mason}, Shawn R. Campagna, Jennifer M. DeBruyn, Dawnie W. Steadman (FEB 2020). Utilizing Metabolomics Toward Time-Dependent Metabolite Monitoring in Different Postmortem Specimens during Human Decomposition. American Academy of Forensic Sciences (AAFS) Anaheim, CA
\item Lois S. Taylor, \textbf{Allison R. Mason}, Ernest C. Bernard, Mary C. Davis, Dawnie W. Steadman, Jennifer M. DeBruyn (FEB 2020). Seasonal Differences in Soil Chemistry and Biology Impacted by Long-term Human Decomposition. American Academy of Forensic Sciences (AAFS) Anaheim, CA
\item Lois S. Taylor, \textbf{Allison R. Mason}, Ernest C. Bernard, Jennifer M. DeBruyn (AUG 2019). [Nematode successional patterns in soils impacted by human decomposition.](https://eco.confex.com/eco/2019/meetingapp.cgi/Paper/79167) Entomological Society of America (ESA)  2019 NA
\end{enumerate}

\hypertarget{awards}{%
\section{\texorpdfstring{\faTrophy Awards}{Awards}}\label{awards}}

\begin{cventries}
    \cventry{The University of Tennessee-Knoxville}{Graduate Student Senate Travel Award}{2022}{}{}\vspace{-4.0mm}
    \cventry{The University of Tennessee-Knoxville}{Graduate Student Senate Travel Award}{2019}{}{}\vspace{-4.0mm}
    \cventry{American Society for Microbiology}{Outstanding Absract Award}{2018}{}{}\vspace{-4.0mm}
    \cventry{American Society for Microbiology}{ASM Student ad Postdoctoral Travel Award}{2018}{}{}\vspace{-4.0mm}
    \cventry{The Universtiy of Tennessee-Knoxville}{Graduate Student Sentate Travel Award}{2018}{}{}\vspace{-4.0mm}
\end{cventries}

\hypertarget{specialized-training}{%
\section{\texorpdfstring{\faBullseye Specialized
Training}{Specialized Training}}\label{specialized-training}}

\begin{cventries}
    \cventry{The University of Michigan}{Software Carpentries Instructor Training}{Nov 2023}{}{}\vspace{-4.0mm}
    \cventry{Chicago, IL}{Introduction to Package Development workshop at posit::conf}{Sep 2023}{}{}\vspace{-4.0mm}
    \cventry{Chigaco, IL}{Package Development Masterclass workshop at posit::conf}{Sep 2023}{}{}\vspace{-4.0mm}
    \cventry{Knoxville, TN}{MICR606 Entering Mentoring}{Jan 2022 - May 2022}{}{}\vspace{-4.0mm}
\end{cventries}

\hypertarget{service}{%
\section{\texorpdfstring{\faHeart Service}{Service}}\label{service}}

\begin{cventries}
    \cventry{U-M Carpentries}{Member}{Jan 2023 - Present}{}{}\vspace{-4.0mm}
    \cventry{Microbiology Graduate Student Association}{Vice President}{Aug 2019 - May 2021}{}{}\vspace{-4.0mm}
    \cventry{University of Tennessee Exhibition of Undergraduate Research and Creative Achievement (EUReCA)}{Symposium Judge}{Apr 2020, Apr 2019}{}{}\vspace{-4.0mm}
    \cventry{University of Tennessee KidsU Fun with Forensics, Adventures in Chemistry}{Instructor}{Jul 2019, Jul 2018}{}{}\vspace{-4.0mm}
    \cventry{Health Occupations Students of America (HOSA) Ohio Regional}{Regional Judge}{May 2017}{}{}\vspace{-4.0mm}
    \cventry{Eastland-Fairfield Bioscience Technologies Capstone Symposium}{Symposium Judge}{Apr 2014}{}{}\vspace{-4.0mm}
\end{cventries}


\label{LastPage}~
\end{document}
