---
surname: Allison R Mason, PhD
position: "Microbiologist"
pronouns: she/her
www: amason30.github.io
github: amason30
linkedin: allisonmason
orcid: 0000-0003-1339-1592
headcolor: 075aa3
date: "`r format(Sys.time(), '%B %Y')`"
output:
  vitae::awesomecv:
    page_total: true
    latex_engine: xelatex
    keep_tex: true
    show_footer: true
  header-includes: 
    - \usepackage{fontawesome}
    - \usepackage{booktabs}
    - \usepackage{longtable}
    - \usepackage{array}
    - \usepackage{multirow}
    - \usepackage{wrapfig}
    - \usepackage{float}
    - \usepackage{colortbl}
    - \usepackage{pdflscape}
    - \usepackage{tabu}
    - \usepackage{threeparttable}
    - \usepackage{threeparttablex}
    - \usepackage[normalem]{ulem}
    - \usepackage{makecell}
    - \usepackage{xcolor}
---

\makeatletter
\def\@sectioncolor{\color{awesome}}
\makeatother

\definecolor{specialblue}{RGB}{7, 90, 163}

```{r setup, include=FALSE}
# options(tinytex.verbose = TRUE)
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(tidyverse)
library(kableExtra)
library(yaml)
library(here)
library(glue)

replace_dollar <- function(x) {
  return(str_replace_all(x,"[$]", "\\$0"))
} # following functions from kelly sovacool https://github.com/kelly-sovacool/latex-cv/blob/main/vitae.Rmd

read_yaml_as_tbl <- function(filepath) {
  read_yaml(filepath) %>%
    map_dfr(function(x) {
      sapply(names(x), function(y) {
        # wrap elements in list if length > 1
        if (length(x[[y]]) > 1) {
          x[[y]] <<- list(x[[y]])
        }
      })
      return(as_tibble_row(x))
    }) %>%
    return()
} 

replace_amps <- function(x) {
  return(str_replace_all(x, "&", "\\\\&"))
}

format_md2tex <- function(x) {
  return(x %>% 
           str_replace_all("_(.*)_", "\\\\textit{\\1}") %>%  # italics
           str_replace_all("\\*\\*(.*)\\*\\*", "\\\\textbf{\\1}") %>% # TODO bold
           str_replace_all('\\+', '\\\\plus') %>% 
           replace_amps()
         )
}

split_md_list <- function(x) {
  return(x %>% 
           str_remove('^- ') %>% 
           str_remove("\n$") %>% 
           str_split('\n- ')
         )
}
```

Summary
=================================

I'm a microbial ecologist with experience in computational biology and management of multivariate projects. My research encompasses soil microbial ecology and terrestrial vertebrate decomposition. I have experience with multiple programming languages, with an expertise in R and execution of microbiome data analysis and package development. I'm passionate about open source science, reproducible research, and teaching computational skill to individuals of all levels.

\faCogs Skills and Expertise
=================================

```{r skilltable, results='markup'}
tribble(
  ~`Computational`, ~`Research`, ~`Laboratory`,
  linebreak("R -- R Markdown -- R Package Development -- Quarto --Git/Github -- Conda -- Unix/zsh"),
  linebreak("Soil sampling/Field research -- Amplicon Sequencing -- Data Analysis/Visualization -- Soil microbiome/necrobiome -- Metatranscriptomics -- Metabolomics -- Biostatistics -- Reproducible Research -- Machine learning"),
  "DNA/RNA extraction -- PCR/qPCR/RT-qPCR -- Cell culture -- Fluorometric assays -- Cell enumeriation -- media/solution preparation -- Cloning -- Gel electrophoresis -- Western blot"
) |>
  kable(booktabs = T, align = 'c', escape = F, format = "latex") |>
  kableExtra::kable_styling(full_width = F, font_size = 9, latex_options = "hold_position") |>
  row_spec(0, bold = T, color = "#075aa3") |>
  row_spec(1, bold = F, color = "#7f7f7f") |>
  column_spec(column = 1:3, width = '4.85cm', latex_valign = "m")
```

\faBarChart Experience
=================================

```{r experience}
read_yaml_as_tbl(here::here("CV/experience.yml")) %>%
  separate(lab, c('lab', 'dept', 'inst'), sep = "<br>") %>%
  mutate(lab = gsub("\\[(.*)\\]\\(.*\\)", "\\1", lab)) %>%
  mutate(why = tasks %>% format_md2tex() %>% split_md_list()) %>%
  detailed_entries(
    what = lab,
    when = dates,
    with = title,
    where = inst,
    why = why,
    .protect = FALSE
  )
```

\faUniversity Education
===================================

```{r edu}
read_yaml_as_tbl(here::here("CV/edu.yml")) %>%
  separate(inst, c('inst', 'dept', 'detail'), sep = "<br>") %>%
  mutate(degree = case_when(degree == "**PhD** Microbiology" ~ "PhD Microbiology",
                            degree == "**BS** Microbiology" ~ "BS Microbiology")) %>%
  detailed_entries(
    what = dept,
    when = dates,
    with = degree,
    where = inst,
    why = detail
  )
```

\faBook Teaching and Mentorship
==============================

\large \textbf{\textcolor{specialblue}{Teaching}}

```{r teaching}
read_yaml_as_tbl(here::here("CV/teaching.yml")) %>%
  rename(course = what) %>%
  separate(where, c('organisation', 'dept'), sep = "<br>") %>%
  mutate(course = format_md2tex(gsub("\\*", "_", course))) %>%
  mutate(course = gsub("<br>", " ", course)) %>%
  mutate(dept = dept %>% replace_amps()) %>%
  detailed_entries(
    with = course,
    where = dept, 
    when = when,
    what = organisation,
    .protect = FALSE
  )
```


\large \textbf{\textcolor{specialblue}{Mentorship}}

```{r mentorship}
read_yaml_as_tbl(here::here("CV/mentorship.yml")) %>%
  separate(what, c("person", "position"), sep = "<br>") %>%
  separate(where, c("dept", "university"), sep = "<br>") %>%
  mutate(position = paste0("\\textit{",position,"}")) %>%
  mutate(person = paste0(person," (",position,")")) %>%
  detailed_entries(
    with = person,
    what = dept,
    where = university,
    when = when,
    .protect = FALSE
  )
```


\faFileText Publications
=============================

```{r pubs, results='asis'}
bib_entries <- read_yaml_as_tbl(here::here("CV/publications.yml"))

raise_asterisk <- function(x) {
  return(str_replace_all(x, "\\*", "\\textsuperscript{*}"))
}



pubs <- bib_entries %>%
  mutate(authors = format_md2tex(authors),
         journal = format_md2tex(gsub("\\*", "_", journal)),
         doi = if_else(doi == "", NA_character_, doi), 
         doi = if_else(is.na(doi), "", paste0("doi: \\href{https://doi.org/",doi,"}{",doi,"}"))) %>%
  mutate(tex = paste0(authors," (",year,"). ",title," ",journal,". ",doi)) %>%
  pull(tex) %>%
  sapply(., function(x) {glue::glue("\\item { x %>% replace_amps() %>% raise_asterisk() }")})

cat('\\small', '\\begin{enumerate}', pubs, '\\end{enumerate}', sep = "\n")
```

\faComments Presentations
==================================

\large \textbf{\textcolor{specialblue}{Talks}}

```{r talks}
read_yaml_as_tbl(here::here("CV/talks.yml")) %>%
  mutate(title = gsub("<br>",". ",title)) %>% 
  mutate(title = gsub("\\*","_",title)) %>% 
  mutate(title = format_md2tex(title)) %>% 
  detailed_entries(
    what = event,
    when = date,
    with = title,
    where = location,
    .protect = FALSE
  )
```

\large \textbf{\textcolor{specialblue}{Posters}}

```{r posters}
read_yaml_as_tbl(here::here("CV/posters.yml")) %>%
  mutate(title = gsub("<br>",". ",title)) %>% 
  mutate(title = gsub("\\(.*\\)","",title)) %>%
  mutate(title = gsub("\\[|\\]","",title)) %>%
  mutate(title = gsub("\\*","_",title)) %>% 
  mutate(title = format_md2tex(title)) %>% 
  detailed_entries(
    what = event,
    when = date,
    with = title,
    where = location,
    .protect = FALSE
  )
```

\faGroup Collaborator Products
====================================

```{r collabs, results = 'asis'}
collab_entries <- read_yaml_as_tbl(here::here("CV/nonfirstauth_contributions.yml"))

remove_links <- function(x) {
  new <- x %>%
          str_replace(., "\\(.*\\)", "") %>%
          str_replace(., "\\[", "") %>%
          str_replace(., "\\]", "")

  return(new)
  }

raise_asterisk <- function(x) {
  return(str_replace_all(x, "\\*", "\\textsuperscript{*}"))
}

pres <- collab_entries %>%
  mutate(authors = format_md2tex(authors), 
         event = format_md2tex(gsub("\\*", "_", event))) %>%
  mutate(event = replace_amps(event),
         title = ifelse(str_detect(title, "\\["), remove_links(title), title)) %>%
  mutate(tex = paste0(authors," (",as.character(date),"). ",title," ",event," ",location)) %>%
  pull(tex) %>%
  sapply(., function(x) {glue::glue("\\item { x %>% replace_amps() %>% raise_asterisk() }")})

cat('\\small', '\\begin{enumerate}', pres, '\\end{enumerate}', sep = "\n")
```

\faTrophy Awards 
================================

```{r awards}
read_yaml_as_tbl(here::here("CV/awards.yml")) %>%
  mutate(where = format_md2tex(gsub("\\*", "_", where))) %>%
  mutate(where = gsub("<br>", " ", where)) %>%
  mutate(award = format_md2tex(gsub("\\*", "_", award))) %>%
  mutate(award = gsub("<br>", " ", award)) %>%

  # mutate(where = gsub("<br>", " ", where)) %>%
  # mutate(where = format_md2tex(gsub("\\*", "_", where))) %>%
  detailed_entries(
    with = award,
    what = where,
    where = year,
    .protect = FALSE
  )
```

\faBullseye Specialized Training
======================================

```{r training}
read_yaml_as_tbl(here::here("CV/development.yml")) %>%
  mutate(where = gsub("<br>", " ", where)) %>%
  mutate(where = gsub("*", "", where)) %>%
  detailed_entries(
    with = what,
    what = where,
    where = when
  )
```

\faHeart Service 
=================================

```{r service}
read_yaml_as_tbl(here::here("CV/service.yml")) %>%
  mutate(where = gsub("<br>", " ", where)) %>%
  mutate(where = gsub("*", "", where)) %>%
  detailed_entries(
    with = what,
    what = where,
    where = dates
  )
```
